### 2011-01-19 Text/paper.tex
Added descriptor but doesn't work till the end.

\section{Steady-state case}
We want to perform understanding of the steady state regime. As well probably it's good idea to
change domain as well, to reduce the length but to insure enough length of the bubble. The
steady-state calculations are performed on $52\mathrm{x}52\mathrm{x}750$ with large enough the
interface.

>>>>

\section{Steady-state case}
We performed different simulations to understand a number of steps required for the problem to come
on the steady-state. The grid to be simulated is $52\mathrm{x}52\mathrm{x}750$ with the initial
width as $6.5$ lattice Boltzmann units together with $\frac{\mathrm{d}P}{\mathrm{d}x}=3
\mathrm{x}10^{-5}$. The simulation was performed for $200000$,$400000$,$600000$ and $800000$ time
iterations. The results are summarised in Table \ref{table:steady:state}. One of the profiles in
the middle of the bubble is shown in Fig. \ref{fig:steady:state:profile:example}.
\begin{table}
\begin{tabular}{|c|c|c|c|}
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$200000$&$0.285$&$0.873$&$0.921$\\
$400000$&$0.274$&$0.873$&$0.920$\\
$600000$&$0.263$&$0.872$&$0.919$\\
$800000$&$0.252$&$0.873$&$0.917$\\
\end{tabular}
\caption{Results for the steady-state case. One can see that $200000$ steps are enough to structure
the bubble. However, the interface is underresolved. That could be the influence of the bubble
length.\label{table:steady:state}}
\end{table}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/bullet.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/example_crossection.eps}\\
\caption{Slice in the middle of the bubble and
three-dimensional example. \label{fig:steady:state:profile:example}}
\end{figure}

To understand the influence of the steady-state case
For the steady-state regime the following parameters were obtained
We want to perform understanding of the steady state regime. As well probably it's good idea to
change domain as well, to reduce the length but to insure enough length of the bubble. The
steady-state calculations are performed on $52\mathrm{x}52\mathrm{x}750$ with large enough the
interface.
